---
title: "R Notebook"
output: html_notebook
Author: Ise Jan Reimering
Reviewer: Joey van den Berg
---


## Libraries

```{r}
install.packages("readxl")
install.packages("tidyverse")
install.packages("googlesheets4")
install.packages("class")
install.packages("caret")
install.packages("ggplot2")

library(readxl)
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
library(ggplot2)
```


## Busines Understanding
With this data there is an attempt to accurately say based on 5 factors whether a house is occupied or empty.

## Data Understanding
To understand the data there is a view of the first 6 rows there is a summary and the internal structure.

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read.csv(ulr)

summary(rawDF)
head(rawDF)
str(rawDF)
```

## Data Preparation
To make a KNN model the data needs to be prepared.Here the data has been normalized. After the normalization the clean dataset was created, a training and a test was made and labels were created for the training and test set. 

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)

str(cleanDF)

summary(cleanDF[,c(1,2,3,4,5))

cntDiag <- table(cleanDF$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag

propDiag

cleanDF$occupancy <- factor(cleanDF$Occupancy, levels = c("0", "1"), labels = c("Occupied", "Empty")) %>% relevel("Empty")
head(cleanDF, 10)

summary(cleanDF[c("Temperature", "Humidity", "Light", "CO2", "HumidityRatio")])

normalize <- function(x) { 
  return ((x - min(x)) / (max(x) - min(x))) 
}

cleanDF_n <- as.data.frame(lapply(cleanDF[,c(1,2,3,4,5)], normalize))

str(cleanDF_n)
summary(cleanDF_n)

clean_train <- cleanDF_n(1:7000, )
clean_test <- cleanDF_n(7001:8143, )

clean_train_target <- cleanDF(1:7000, 6)
clean_test_target <- cleanDF(7001:8143, 6)
```


## Modeling
Here the KNN model was created with the prepared data.

```{r}
m1 <- knn(train = clean_train, test = clean_test, cl == clean_train_target, k = 91)
head(m1)

table(clean.test.target, m1)
```


## Evaluation and Deployment
The model will be evaluated and deployed here.

```{r}
confusionMatrix(m1, clean_test_target, negative = NULL, dnn = c("Prediction", "True"))
```


reviewer adds suggestions for improving the model
